Estimating Carrying Capacity for Chinook Parr using Quantile Random Forest Models

### 2020-06-10 analysis/paper/paper.Rmd
test commit. Minor edits to biological expectations paragraph.

The results of the QRF parr capacity model for spring/summer Chinook salmon meet many biological expectations. Focusing on the partial dependence plots (Figure \@ref(fig:pdp-figure)), the QRF model predicts capacity to increase when the wetted width, discharge and the width-to-depth ratio grow, when temperatures are cooler, when there is less fine sediment, when there is more fish cover, when channel unit frequency increases and when the standard deviation of the wetted depth (a proxy for complexity) increases. These are all patterns that emerged from the fish-habitat data, and those fish-habitat relationships match what has been found qualitatively in many other studies (**need more citations??**) [@Mossop2006].

>>>>

The results of the QRF parr capacity model for spring/summer Chinook salmon meet many biological expectations. Focusing on the partial dependence plots (Figure \@ref(fig:pdp-figure)), the QRF model predicts capacity to increase when the wetted width, discharge and the width-to-depth ratio grow, when temperatures are cooler, when there is less fine sediment, when there is more fish cover, when channel unit frequency increases and when the standard deviation of the wetted depth (a proxy for complexity) increases. These are all patterns that emerged from the fish-habitat data, and where available, those fish-habitat relationships match what has been found qualitatively in other studies (**need more citations??**) [@Mossop2006].
